Hot and fresh: Pervasive climate stressors of seagrass in a large Gulf coast estuary

### 2023-08-24 manu-draft.qmd
added nickerson ref

@@

![Trends from 1974 to 2022 for salinity and temperature measurements at long-term monitoring stations in Tampa Bay. Results for (a) seasonal Kendall tests by station and monitoring location (top or bottom of the waer column) are shown in (a) with color and shape corresponding to the estimated annual slope as change per year (yr-1).  Summarized seasonal trends by month are shown for (b) top and (c) bottom measurements as the percent of stations in each bay segment with significant decreasing (salinity) or increasing (temperature) trends.  Bay segment outlines are shown in (a); OTB (northwest): Old Tampa Bay, HB (northeast): Hillsborough Bay, MTB: Middle Tampa Bay, LTB: Lower Tampa Bay.  ](figs/kendall.png){#fig-kendall}

@@

Summary of mixed-effects models evaluating increases in the number of days each year from 1974 to 2022 when salinity or temperature was below or above critical thresholds, respectively.  The slope estimates in the "Both" column indicate trends in the number of days when both salinity and temperature were below or above critical thresholds. ** p < 0.005, * p < 0.05, - no model. OTB (northwest): Old Tampa Bay, HB (northeast): Hillsborough Bay, MTB: Middle Tampa Bay, LTB: Lower Tampa Bay.
```{r}
mixtab
```

@@

Number of days at the beginning and end of the period of record when salinity or temperature was below or above critical thresholds, respectively.  Values are the estimated mean number of days (plus standard error) from 1974 to 2022.  Columns for "Both" indicate the estimated number of days when both salinity and temperature were below or above critical thresholds.  Note that not all models are significant (see (table 1)). ** p < 0.005, * p < 0.05, - no model. OTB (northwest): Old Tampa Bay, HB (northeast): Hillsborough Bay, MTB: Middle Tampa Bay, LTB: Lower Tampa Bay.
```{r}
daytab
```

>>>>

Background: SST trends in Tampa Bay w/ EPC data, WFS, and deep GOM [@nickerson2023] showed that 1975 to 2022 trend for EPC was notable, but less so from 1998 to 2022. Also noted the trend was most pronounced in the winter, see Fig 3.

@@

![Trends from 1974 to 2022 for salinity and temperature measurements at long-term monitoring stations in Tampa Bay. Results for (a) seasonal Kendall tests by station and monitoring location (top or bottom of the waer column) are shown in (a) with color and shape corresponding to the estimated annual slope as change per year (yr-1). Summarized seasonal trends by month are shown for (b) top and (c) bottom measurements as the percent of stations in each bay segment with significant decreasing (salinity) or increasing (temperature) trends. Bay segment outlines are shown in (a); OTB (northwest): Old Tampa Bay, HB (northeast): Hillsborough Bay, MTB: Middle Tampa Bay, LTB: Lower Tampa Bay.](figs/kendall.png){#fig-kendall}

@@

Summary of mixed-effects models evaluating increases in the number of days each year from 1974 to 2022 when salinity or temperature was below or above critical thresholds, respectively. The slope estimates in the "Both" column indicate trends in the number of days when both salinity and temperature were below or above critical thresholds. \*\* p \< 0.005, \* p \< 0.05, - no model. OTB (northwest): Old Tampa Bay, HB (northeast): Hillsborough Bay, MTB: Middle Tampa Bay, LTB: Lower Tampa Bay.

```{r}
mixtab
```

@@

Number of days at the beginning and end of the period of record when salinity or temperature was below or above critical thresholds, respectively. Values are the estimated mean number of days (plus standard error) from 1974 to 2022. Columns for "Both" indicate the estimated number of days when both salinity and temperature were below or above critical thresholds. Note that not all models are significant (see (table 1)). \*\* p \< 0.005, \* p \< 0.05, - no model. OTB (northwest): Old Tampa Bay, HB (northeast): Hillsborough Bay, MTB: Middle Tampa Bay, LTB: Lower Tampa Bay.

```{r}
daytab
```
